{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-08-15 swmp_noise.Rnw
almost ready to start discussion

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0.3, 0.7),
    breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Hours') +
  ylab('Days') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = brewer.pal(11, 'Spectral'), limits = c(1, 1.5), 
    labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Hours') +
  ylab('Days') + 
  theme_bw() +
  mat_theme

@@

% example of extreme scenario
\centering\vspace*{\fill}
<<extreme, eval = F, echo = F, cache = T, fig.width = 7, fig.height = 6.5, fig.cap = 'An extreme example of results from the weighted regression with decreasing window widths.  Results are for a simulated time series with a diurnal tidal component, no effect of tidal advection ($DO_{adv} = 0$), and an observed \\ac{DO} signal dominated only by a diel component ($DO_{bio} = 2$, $\\epsilon_{obs} = 0$, $\\epsilon_{pro} = 0$).  Window widths varied form 2 to 40 days.  See \\cref{do_tid,do_mtd,do_dtd,do_obs} for notation.'>>=
######
# examples of how detiding works

# combination grid, used for systematic sims
load('comb_grd.RData')

# load predicted/normalized data
load('prdnrm.RData')

# get results from prdnrm corresponding to a given window value in which_wins
# rownames in which_wins are used to iterate through prdnrm
names(comb_grd)[names(comb_grd) %in% 'dec_time'] <- 'dec_win'

sel_vec <- with(comb_grd,
  tide_cat %in% 'Diurnal' &
  bio_rng %in% 2 &
  tide_assoc %in% 0 &
  err_rng_obs %in% 0 &
  err_rng_pro %in% 0
  )

# sub of comb_grd 
comb_tmp <- comb_grd[sel_vec, ]
comb_tmp$L1 <- rownames(comb_tmp)
# sub of prdnrm list, name list with rownames of comb_grd for merge
prd_tmp <- prdnrm[sel_vec]
names(prd_tmp) <- rownames(comb_tmp)

# melt predictions and merge with comb_tmp
prd_tmp <- melt(prd_tmp, id.var = names(prd_tmp[[1]]))
prd_tmp <- merge(prd_tmp, comb_tmp, by = 'L1', all.x = T)

# create residual vector
prd_tmp$DO_res <- with(prd_tmp, DO_obs - DO_prd)
# dobule windows since theyre halves
prd_tmp$dec_win <- as.character(2 * prd_tmp$dec_win)

levs <- c('DO_adv', 'DO_obs', 'DO_prd',
  'DO_nrm', 'DO_dtd')
to.plo <- melt(prd_tmp, id.var = c('Day', 'dec_win', 'tide_cat'),
  measure.var = levs
  )
to.plo$variable <- factor(to.plo$variable, levels = levs)
levs <- as.character(c(2, 10, 20, 30, 40))
to.plo$dec_win <- factor(to.plo$dec_win, labels = levs, levels = levs)

ylab<-expression(paste('DO (mg ',L^-1,')'))

p1 <- ggplot(to.plo, aes(x = Day, y = value, 
    group = dec_win, colour = dec_win)) +
  geom_line(size = 1) +
  facet_wrap(~ variable, scales = 'free_y', ncol = 1) + 
  theme_bw() +
  ylab(ylab) + 
  scale_colour_manual('Window', values = brewer.pal(5, 'Spectral')) +
  theme(legend.position = 'top')

facet_wrap_labeller(p1, labels = c(
  expression(italic(DO [adv])),
  expression(italic(DO [obs])),
  expression(italic(DO [tid])),
  expression(italic(DO [mtd])),
  expression(italic(DO [dtd]))
  ))
@
\vfill
\clearpage

@@

% example from SAPDC
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism and \\ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Sapelo Island station using a weighted regression with a window of thirty days and tidal height proportion of one.'>>=
######
# SAPDC example

load('met_ls_inst.RData')
load('met_ls.RData')
load('case_grds.RData')

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-03-20','2012-03-29')) 
sel_vec <- with(case_grds, which(Day == 30 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
inst_subs <- met_ls_inst[[grep(sel_vec, names(met_ls))]]

@@

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_dtd, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,9)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

@@

# ######
# # table of case study characteristics
# # uses local files not in project....
# 
# cases <- c('ELKVM','PDBBY', 'RKBMB', 'SAPDC')
# 
# ##
# # get amps (m) of dominant tidal constituents
# 
# files <- list.files('M:/wq_models/SWMP/raw/rproc/proc5/', 
#   pattern = paste(cases, collapse = '|'), 
#   full.names = T)
# file_ls <- list()
# for(file in files){
#   load(file)
#   nm <- gsub('.RData', '', basename(file))
#   cat(nm, '\t')
#   tmp <- get(nm)
#   mod <- oce::tidem(tmp$Depth, tmp$DateTimeStamp, 
#     constituents = c('P1', 'O1', 'M2', 'S2'))
#   const <- attr(mod, 'data')$amplitude[-1]
#   names(const) <- attr(mod, 'data')$name[-1]
#     
#   file_ls[[nm]] <- const
#   }
# tide_comps<- data.frame(do.call('rbind', file_ls))
# tide_comps$site <- rownames(tide_comps)
# 
# ##
# # get mean daily DO range
# 
# files <- list.files('M:/wq_models/SWMP/raw/rproc/proc5/', 
#   pattern = paste(cases, collapse = '|'), 
#   full.names = T)
# file_ls <- list()
# for(file in files){
#   load(file)
#   nm <- gsub('.RData', '', basename(file))
#   cat(nm, '\t')
#   tmp <- get(nm)
#   file_ls[[nm]] <- tmp
#   }
# 
# daily_do <- adply(
#   file_ls, 1, 
#   function(x) {
#     x$jday <- format(x$DateTimeStamp, '%j')
#     out <- ddply(x,
#       .variable = 'jday',
#       .fun = function(y){
#         if(sum(is.na(y$DO_mgl)) == length(y$DO_mgl)) NA
#         else {
#           rng <- diff(c(min(y$DO_mgl, na.rm = T), 
#             max(y$DO_mgl, na.rm = T)))
#           avg <- mean(y$DO_mgl, na.rm = T)
#           c(rng, avg)
#           }
#         }
#       )
#     colMeans(out[, -1], na.rm = T)
#     }, 
#   .progress = 'tk'
#   )
# names(daily_do) <- c('site', 'daily_rng', 'daily_avg')
# 
# ##
# # get metab summaries
# 
# # metab data
# load('met_ls.RData')
# 
# met_sum <- adply(matrix(cases, ncol = 1),
#   1,
#   .fun = function(x){
#     
#     met <- met_ls[[x]][, c('Pg', 'Rt', 'NEM')]
#     colMeans(met, na.rm = T)
#      
#     }
#   )
# met_sum$X1 <- NULL
# met_sum$site <- cases
# 
# ##
# # combine data 
# # tide_comps, daily_do, met_sum
# 
# to_tab <- cbind(tide_comps, daily_do, met_sum)
# to_tab <- to_tab[, !names(to_tab) %in% 'site']
# 
# case_tab <- to_tab
# save(case_tab, file = 'case_tab.RData')

@@

# # metab and inst flux data
# load('met_ls.RData')
# # load('met_ls_inst.RData')
# load('case_grds.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files(getwd(), '_wtreg_[0-9]*.RData')
# cor_res <- alply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(x)
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_nrm, Tide)
#       )
#     
#     # get tidal range for metabolic day/night periods from flux_in
#     # for correlation with daily integrated metab
#     tide_rngs <- ddply(dat_in, 
#       .variables = c('met.date'),
#       .fun = function(x){
#         
#         # mean tidal derivative for day hours
#         sunrise <- mean(diff(x[x$variable %in% 'sunrise', 'Tide'], 
#           na.rm = T))
#         
#         # mean tidal derivative for night hours
#         sunset <- mean(diff(x[x$variable %in% 'sunset', 'Tide'], 
#           na.rm = T))
#         if(sunrise == 'Inf') sunrise <- NA
#         if(sunset == 'Inf') sunset <- NA
#         
#         # mean tidal derivative for metabolic day
#         daytot <- mean(diff(x$Tide, na.rm = T))
#         
#         c(daytot, sunrise, sunset)
#         
#         }
#       )
#     names(tide_rngs) <- c('Date','daytot', 'sunrise', 'sunset')
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     dat_in <- merge(dat_in, tide_rngs, by = 'Date', all.x = T)
#     
#     # as list for all metab correlations
#     # Pg values correlated with tidal range during sunlight hours
#     # Rt values correlated with tidal range during night hours
#     # NEM values correlated with metabolic daily tidal range
#     met_cor <- list(
#       
#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),
#     
#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#     
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#     
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#     
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#     
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)
#         )
#       
#       )
#     
#     # DO and metab corrs combined
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       met_cor)
#     
#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
#     names(res_sum) <- c('var', 'cor', 'pval')
# 
#     res_sum
#     
#   })
# names(cor_res) <- case_regs
# 
# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))
# 
# # merge with case_grds
# case_grds$wins <- as.numeric(row.names(case_grds))
# cor_res <- merge(cor_res, case_grds, by = 'wins', all.x = T)
# 
# # create columns for variable (DO, flux, etc.) and sub variable (obs, dtd)
# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)
# cor_res$var <- gsub('_.*$', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')
# 
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = dec_time, y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = dec_time, y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(hour ~ site + var) +
#   ylim(c(-1, 1))

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, dec_time == 4 & hour == 6 & Tide == 1), ]

@@

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations, instantaneous \\ac{DO} flux, and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after detiding with weighted regression.  \\ac{DO} values are correlated with predicted tidal height at each observation, \\ac{DO} flux values are correlated with tidal change between observations, and metabolism estimates are correlated with mean tidal change between observations during day, night, or total, day periods for production, respiration, and net metabolism respectively.  Total day periods were defined as the approximate 24 hours between sunrises for two calendar days, where day was the time from sunrise to sunset and night was the following time from sunset to sunrise.  Results are for weighted regressions using a window of thirty days and tidal height proportion of one.'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# # metab estimates for each wtreg
# load('met_ls.RData')
# 
# # subset metab estimates by 30 day window and tide prop 1
# load('case_grds.RData')
# sel_vec <- with(case_grds, which(dec_time == 4 & hour == 6 & Tide == 1))
# 
# met_sub <- met_ls[grep(sel_vec, names(met_ls))]
# 
# met_comp <- ldply(met_sub, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
# 
# save(met_comp, file = 'met_comp.RData')

>>>>

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0.3, 0.7),
    breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(1, 1.5), 
    labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

@@

@@

% example from RKBMB
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism (top) and \\ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}) is on the bottom plot. Results are for the Rookery Bay station in July, 2012 using a weighted regression with a window of eight days, six hours within each day, and tidal height proportion of one.'>>=
######
# RKBMB example

load('met_ls.RData')
load('case_grds.RData')

# subsets by case. date range, window comb
case <- 'RKBMB'
dat.rng<-as.Date(c('2012-07-01','2012-07-31')) 
sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

@@

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,9)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

% plots of metab for all cases, period of obs
\centering\vspace*{\fill}
<<case_ex2, cache = T, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = ''>>=
######
# metab before/after, all case studies

load('met_ls.RData')
load('case_grds.RData')

# subsets by case. date range, window comb
sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,9)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

@@

# ######
# # table of case study characteristics
# # uses local files not in project....
# 
# cases <- c('ELKVM','PDBBY', 'RKBMB', 'SAPDC')
# 
# ##
# # get amps (m) of dominant tidal constituents
# 
# files <- list.files('M:/wq_models/SWMP/raw/rproc/proc5/', 
#   pattern = paste(cases, collapse = '|'), 
#   full.names = T)
# file_ls <- list()
# for(file in files){
#   load(file)
#   nm <- gsub('.RData', '', basename(file))
#   cat(nm, '\t')
#   tmp <- get(nm)
#   mod <- oce::tidem(tmp$Depth, tmp$DateTimeStamp, 
#     constituents = c('P1', 'O1', 'M2', 'S2'))
#   const <- attr(mod, 'data')$amplitude[-1]
#   names(const) <- attr(mod, 'data')$name[-1]
#     
#   file_ls[[nm]] <- const
#   }
# tide_comps<- data.frame(do.call('rbind', file_ls))
# tide_comps$site <- rownames(tide_comps)
# 
# ##
# # get mean daily DO range
# 
# files <- list.files('M:/wq_models/SWMP/raw/rproc/proc5/', 
#   pattern = paste(cases, collapse = '|'), 
#   full.names = T)
# file_ls <- list()
# for(file in files){
#   load(file)
#   nm <- gsub('.RData', '', basename(file))
#   cat(nm, '\t')
#   tmp <- get(nm)
#   file_ls[[nm]] <- tmp
#   }
# 
# daily_do <- adply(
#   file_ls, 1, 
#   function(x) {
#     x$jday <- format(x$DateTimeStamp, '%j')
#     out <- ddply(x,
#       .variable = 'jday',
#       .fun = function(y){
#         if(sum(is.na(y$DO_mgl)) == length(y$DO_mgl)) NA
#         else {
#           rng <- diff(c(min(y$DO_mgl, na.rm = T), 
#             max(y$DO_mgl, na.rm = T)))
#           avg <- mean(y$DO_mgl, na.rm = T)
#           c(rng, avg)
#           }
#         }
#       )
#     colMeans(out[, -1], na.rm = T)
#     }, 
#   .progress = 'tk'
#   )
# names(daily_do) <- c('site', 'daily_rng', 'daily_avg')
# 
# ##
# # get metab summaries
# 
# # metab data
# # this is for observed data so, doesn't matter which index number
# load('met_ls.RData')
# 
# met_sum <- adply(matrix(cases, ncol = 1),
#   1,
#   .fun = function(x){
#     
#     met <- met_ls[[paste0(x, '_wtreg_1.RData')]][, c('Pg', 'Rt', 'NEM')]
#     colMeans(met, na.rm = T)
#      
#     }
#   )
# met_sum$X1 <- NULL
# met_sum$site <- cases
# 
# ##
# # combine data 
# # tide_comps, daily_do, met_sum
# 
# to_tab <- cbind(tide_comps, daily_do, met_sum)
# to_tab <- to_tab[, !names(to_tab) %in% 'site']
# 
# case_tab <- to_tab
# save(case_tab, file = 'case_tab.RData')

@@

# # metab and inst flux data
# load('met_ls.RData')
# # load('met_ls_inst.RData')
# load('case_grds.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files('wtreg', '_wtreg_[0-9]*.RData')
# cor_res <- alply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(paste0('wtreg/', x))
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_nrm, Tide)
#       )
#     
#     # get tidal range for metabolic day/night periods from flux_in
#     # for correlation with daily integrated metab
#     tide_rngs <- ddply(dat_in, 
#       .variables = c('met.date'),
#       .fun = function(x){
#         
#         # mean tidal derivative for day hours
#         sunrise <- mean(diff(x[x$variable %in% 'sunrise', 'Tide'], 
#           na.rm = T))
#         
#         # mean tidal derivative for night hours
#         sunset <- mean(diff(x[x$variable %in% 'sunset', 'Tide'], 
#           na.rm = T))
#         if(sunrise == 'Inf') sunrise <- NA
#         if(sunset == 'Inf') sunset <- NA
#         
#         # mean tidal derivative for metabolic day
#         daytot <- mean(diff(x$Tide, na.rm = T))
#         
#         c(daytot, sunrise, sunset)
#         
#         }
#       )
#     names(tide_rngs) <- c('Date','daytot', 'sunrise', 'sunset')
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     dat_in <- merge(dat_in, tide_rngs, by = 'Date', all.x = T)
#     
#     # as list for all metab correlations
#     # Pg values correlated with tidal range during sunlight hours
#     # Rt values correlated with tidal range during night hours
#     # NEM values correlated with metabolic daily tidal range
#     met_cor <- list(
#       
#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),
#     
#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#     
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#     
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#     
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#     
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)
#         )
#       
#       )
#     
#     # DO and metab corrs combined
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       met_cor)
#     
#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
#     names(res_sum) <- c('var', 'cor', 'pval')
# 
#     res_sum
#     
#   })
# names(cor_res) <- case_regs
# 
# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))
# 
# # merge with case_grds
# case_grds$wins <- as.numeric(row.names(case_grds))
# cor_res <- merge(cor_res, case_grds, by = 'wins', all.x = T)
# 
# # create columns for variable (DO, flux, etc.) and sub variable (obs, dtd)
# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)
# cor_res$var <- gsub('_.*$', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')
# 
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = dec_time, y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = dec_time, y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(hour ~ site + var) +
#   ylim(c(-1, 1))

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, dec_time == 8 & hour == 6 & Tide == 1), ]

@@

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after (detided) detiding from weighted regression.  \\ac{DO} values are correlated with predicted tidal height at each observation, whereas metabolism estimates are correlated with mean tidal height change between observations during day, night, or total day periods for production, respiration, and net metabolism, respectively.'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# # metab estimates for each wtreg
# load('met_ls.RData')
# 
# # subset metab estimates by 30 day window and tide prop 1
# load('case_grds.RData')
# sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))
# 
# met_sub <- met_ls[grep(sel_vec, names(met_ls))]
# 
# met_comp <- ldply(met_sub, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
# 
# save(met_comp, file = 'met_comp.RData')
